\documentclass[a4paper,11pt]{article}

% Setting up the geometry for balanced margins
\usepackage[scale=0.85]{geometry}
\usepackage{url}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Set all links to black for black-and-white CV
\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black, citecolor=black}

% Setting main font to Times New Roman
\usepackage{mathptmx}
% Add setspace package for line spacing
\usepackage{setspace}

% Customizing section titles
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{6pt}

% Centered column type for tabularx
\newcolumntype{C}{>{\centering\arraybackslash}X}

% Fixed jobshort environment
\newcommand{\jobshort}[3]{
    \begin{tabularx}{\linewidth}{@{}l r@{}}
    \textbf{#1} & #2 \\
    \multicolumn{2}{@{}p{\linewidth}@{}}{#3}
    \end{tabularx}
}

% Custom environment for detailed job/project listings
\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l r@{}}
    \textbf{#1} & #2 \\[2pt]
    \end{tabularx}
    \begin{itemize}[nosep,leftmargin=1.5em,itemsep=2pt,label=--]
    }
    {
    \end{itemize}
    }

% Begin document
\begin{document}
\pagestyle{empty}

% FIXED TITLE SECTION
\begin{center}
\LARGE{Phan Xuân Thái} \\[5pt]
\small{\href{mailto:phanxuanthai2004@gmail.com}{phanxuanthai2004@gmail.com} $|$ 
\href{tel:0934904613}{0934904613} $|$ 
\href{https://github.com/hidr0c}{\underline{github.com/hidr0c}} $|$ 
\href{https://www.linkedin.com/in/xuân-thái-phan-bab693352/}{\underline{linkedin.com/phan-xuan-thai}} 
} \\[2pt]
\end{center}
% Add extra vertical space between title and first section
\vspace{1.5em}

% Summary
\section{Summary}
\begin{spacing}{1.05}
Proactive and motivated junior Software Engineering student at HUFLIT with a solid foundation in front-end development. Experienced with JavaScript, TypeScript, React, Next.js, and Tailwind CSS through personal and academic projects. Continuously building projects to strengthen my skills and write clean, maintainable code. Looking for a front-end fresher or internship position to gain practical experience, contribute to real-world products, and continue learning from a professional team.
\end{spacing}

% Skills
\section{Skills}
\begin{spacing}{1.05}
\textbf{Programming Languages:} JavaScript, TypeScript, C\#, HTML/CSS (SCSS), Dart \\
\textbf{Frameworks / Libraries:} Bootstrap 5, React, Next.js, Tailwind CSS, ASP.NET, Flutter \\
\textbf{Tools:} Visual Studio 2022, Git, Visual Studio Code \\
\textbf{Soft Skills:} Event planning and organization, Team collaboration and communication, Time management and problem-solving \\
\end{spacing}

% Education
\section{Education}
\begin{spacing}{1.05}
\begin{tabularx}{\linewidth}{@{}l@{}}
\textbf{Ho Chi Minh City University of Foreign Languages and Information Technology (HUFLIT)} \\
\normalsize\textit{October 2022 -- Present} \\
Software Engineering -- Junior
\end{tabularx}
\end{spacing}

% Projects
\section{Projects}
\begin{spacing}{1.05}
% Project 1
\begin{minipage}[t]{\linewidth}
  \begin{tabularx}{\linewidth}{@{}l r@{}}
    \textbf{TUYU Archives} & \hspace*{0.63\linewidth}\normalsize\textit{26/11/2024 – 03/07/2025} \\
  \end{tabularx}
  \begin{tabularx}{\linewidth}{@{}l r@{}}
  \normalsize\textit {TypeScript, Next.js, Tailwind CSS, Google Drive API}& \hspace*{0.255\linewidth}\href{https://github.com/hidr0c/tuyu-archives}{\normalsize\textit{github.com/hidr0c/tuyu-archives}}\\
  \end{tabularx}
  \textbf{Website:} \href{https://tuyu-archives-pied.vercel.app}{\normalsize\textit{https://tuyu-archives-pied.vercel.app}}  
  \begin{itemize}[nosep,leftmargin=1.2em,itemsep=2pt]
  \item Built a video streaming app with Next.js + React.
  \item Integrated Google Drive API for video and subtitle retrieval (.webm, .mp4, .mkv).
  \item Developed \textbf{EnhancedVideoPlayer} with:
  \begin{itemize}
    \item Playlist 
    \item Dynamic subtitle loading (with CORS handling)
    \item Built-in: play, pause, volume, fullscreen
  \end{itemize}
  \item Created REST APIs for managing local and Drive-based videos.
  \item Refactored legacy codebase for scalability and type safety with TypeScript.
  \end{itemize}
\end{minipage}

\vspace{0.5em}

% Project 2
\begin{minipage}[t]{\linewidth}
  \begin{tabularx}{\linewidth}{@{}l r@{}}
    \textbf{PXT Food Store} & \hspace*{0.63\linewidth}\normalsize\textit{21/03/2025 – 31/03/2025} \\
  \end{tabularx}
  \begin{tabularx}{\linewidth}{@{}l r@{}}
  \normalsize\textit{Flutter, Dart, REST API, Firebase} & \hspace*{0.405\linewidth} {\normalsize\textit{github.com/hidr0c/PXTFoodStore}}\\
  \end{tabularx}
 \begin{itemize} [nosep,leftmargin=1.2em,itemsep=2pt]
  \item Developed a cross-platform food ordering app with Flutter, supporting Android, iOS, web, and desktop.
  \item Integrated Firebase (Authentication, Firestore, Storage) for secure login, real-time data, and image handling.
  \item Designed a custom Material UI with responsive layouts, Google Fonts, and multi-language support.
  \item Managed app state and cart logic using Provider; enabled persistent cart and order history with shared preferences.
  \item Added review/rating system, image uploads, and admin features for order and inventory management.
\end{itemize}



  
\end{minipage}
\end{spacing}

% Activities
\section{Activities}
\begin{spacing}{1.05}
\begin{tabularx}{\linewidth}{@{}l r@{}}
  \textbf{MSOC Tournament} & \hspace*{0.54\linewidth}\normalsize\textit{October 2023 -- December 2024} \\
\end{tabularx}
\begin{itemize}[nosep,leftmargin=1.2em,itemsep=2pt]
  \item Team Leader, Project Management
  \item Led a student-focused maimai game tournament in partnership with Dream Games Tan Phu. Planned, coordinated, and managed event operations, communication, and team tasks. Attracted strong participation and received positive partner feedback. 
  \item Full article on \href{https://www.linkedin.com/feed/update/urn:li:activity:7300042302784233472/}{\underline{LinkedIn}}.
\end{itemize}
\end{spacing}



% Footer
\vspace*{\fill}
\end{document}